---
title: "Recruit Restaurant Visitor Forecasting"
output: html_document
---

```{r message=FALSE}
library(lubridate)
```

## Description

Running a thriving local restaurant isn't always as charming as first impressions appear. There are often all sorts of unexpected troubles popping up that could hurt business.

One common predicament is that restaurants need to know how many customers to expect each day to effectively purchase ingredients and schedule staff members. This forecast isn't easy to make because many unpredictable factors affect restaurant attendance, like weather and local competition. It's even harder for newer restaurants with little historical data.

Recruit Holdings has unique access to key datasets that could make automated future customer prediction possible. Specifically, Recruit Holdings owns Hot Pepper Gourmet (a restaurant review service), AirREGI (a restaurant point of sales service), and Restaurant Board (reservation log management software).

In this competition, you're challenged to use reservation and visitation data to predict the total number of visitors to a restaurant for future dates. This information will help restaurants be much more efficient and allow them to focus on creating an enjoyable dining experience for their customers.

## Data

```{r}
air_reserve  <- read.csv("input/restaurant/air_reserve.csv", stringsAsFactors = F)
hpg_reserve  <- read.csv("input/restaurant/hpg_reserve.csv", stringsAsFactors = F)
air_stores   <- read.csv("input/restaurant/air_store_info.csv", stringsAsFactors = F,fileEncoding = "UTF-8")
hpg_stores   <- read.csv("input/restaurant/hpg_store_info.csv")
store_visits <- read.csv("input/restaurant/air_visit_data.csv")
holydays     <- read.csv("input/restaurant/date_info.csv")
store_relation <- read.csv("input/restaurant/store_id_relation.csv")

```

## Get more info about stores

```{r}
# Order info about stores
stores<-air_stores
# Get place of area
stores$city_ward<-gsub("^((?:\\S+\\s+){1}\\S+).*","\\1",stores$air_area_name)
stores$ini_place<-nchar(stores$city_ward) + 2
stores$end_place<-nchar(stores$air_area_name)
stores$place<-substr(stores$air_area_name,stores$ini_place,stores$end_place)
# Get city of area
stores$city<-gsub("^((?:\\S+\\s+){0}\\S+).*","\\1",stores$air_area_name)
# Get ward of area
stores$ini_ward<-nchar(stores$city) + 2
stores$end_ward<-nchar(stores$city_ward)
stores$ward<-substr(stores$city_ward,stores$ini_ward,stores$end_ward)
# Get if stores have hpg system
stores<-merge(stores,store_relation,by = "air_store_id",all = TRUE)
stores$hpg_system <- 1
stores$hpg_system[is.na(stores$hpg_store_id)] <- 0
# Clean store table
stores<-stores[,c("air_store_id","air_genre_name","city","ward","place","hpg_system")]

```

## Get more info about dates

```{r}
# Order info about holydays
calendar <- holydays
tail(calendar)
# Obtener dia y mes de la fecha
calendar$day<-day(as.Date(calendar$calendar_date))
calendar$month<-month(as.Date(calendar$calendar_date))
calendar$month_day <- (calendar$month * 100) + calendar$day
calendar$month_name <- month(as.Date(calendar$calendar_date),label = TRUE)
# obtener dias del golden week 
calendar$golden_week <- 0
calendar[calendar$month_day>=429 & calendar$month_day<=505,]$golden_week <- 1
calendar[calendar$golden_week==1,]
# Clean data of calendar
calendar<-calendar[,c("calendar_date","day_of_week","month_name","holiday_flg","golden_week")]
```

## Get more info about dates

```{r}
# Order info about holydays
calendar <- holydays
tail(calendar)
# Obtener dia y mes de la fecha
calendar$day<-day(as.Date(calendar$calendar_date))
calendar$month<-month(as.Date(calendar$calendar_date))
calendar$month_day <- (calendar$month * 100) + calendar$day
calendar$month_name <- month(as.Date(calendar$calendar_date),label = TRUE)
# obtener dias del golden week 
calendar$golden_week <- 0
calendar[calendar$month_day>=429 & calendar$month_day<=505,]$golden_week <- 1
calendar[calendar$golden_week==1,]
# Clean data of calendar
calendar<-calendar[,c("calendar_date","day_of_week","month_name","holiday_flg","golden_week")]
```

## Get more info about reserves

```{r}
### Obtener las visitas registradas por air system ###

reserves <- air_reserve
# obtener dia de la visita
reserves$ocurrences <- 1
reserves$visit_date <- as.Date(reserves$visit_datetime)
reserves$reserve_date <- as.Date(reserves$reserve_datetime)
reserves$anticipation <- as.numeric(reserves$visit_date - reserves$reserve_date)
reserves$id <- paste(reserves$air_store_id,reserves$visit_date,sep = "_")
# Obtener visitas por dia y por tienda
reserves00 <- aggregate(x=reserves$reserve_visitors, 
          by= list(id=reserves$id),FUN=sum)
reserves00$air_visitors<-reserves00$x
reserves00$x <- NULL
tail(reserves00)
# Obtener numero de reservas por dia y por tienda
reserves01 <- aggregate(reserves$ocurrences, 
                        by= list(id=reserves$id),FUN=sum)
reserves01$air_reserves<-reserves01$x
reserves01$x <- NULL
tail(reserves01)
# Obtener media de anticipación por dia y por tienda
reserves02 <- aggregate(reserves$anticipation, 
                        by= list(id=reserves$id),FUN=mean)
reserves02$air_anticipation<-reserves02$x
reserves02$x <- NULL
# Realizar el join
reserves <- merge(reserves00,reserves01,by="id")
reserves <- merge(reserves,reserves02,by="id")
rm(reserves00,reserves01,reserves02)

### Obtener las visitas registradas por hpg system ###

reshpg<-merge(store_relation,hpg_reserve,by="hpg_store_id")
# obtener dia de la visita
reshpg$ocurrences <- 1
reshpg$visit_date <- as.Date(reshpg$visit_datetime)
reshpg$reserve_date <- as.Date(reshpg$reserve_datetime)
reshpg$anticipation <- as.numeric(reshpg$visit_date - reshpg$reserve_date)
reshpg$id <- paste(reshpg$air_store_id,reshpg$visit_date,sep = "_")
# Obtener visitas por dia y por tienda
reshpg00 <- aggregate(x=reshpg$reserve_visitors, 
                      by= list(id=reshpg$id),FUN=sum)
reshpg00$hpg_visitors<-reshpg00$x
reshpg00$x <- NULL
# Obtener numero de reservas por dia y por tienda
reshpg01 <- aggregate(reshpg$ocurrences, 
                        by= list(id=reshpg$id),FUN=sum)
reshpg01$hpg_reserves<-reshpg01$x
reshpg01$x <- NULL
# Obtener media de anticipación por dia y por tienda
reshpg02 <- aggregate(reshpg$anticipation, 
                        by= list(id=reshpg$id),FUN=mean)
reshpg02$hpg_anticipation<-reshpg02$x
reshpg02$x <- NULL
# Realizar el join
reshpg <- merge(reshpg00,reshpg01,by="id")
reshpg <- merge(reshpg,reshpg02,by="id")
rm(reshpg00,reshpg01,reshpg02)

```

## Join Everything

```{r}
visits <- merge(store_visits,calendar,by.x = 'visit_date', by.y = 'calendar_date')
visits <- merge(visits,stores,by = 'air_store_id')
visits$id <- paste(visits$air_store_id,visits$visit_date,sep = "_")

visits <- merge(visits,reserves,by="id", all.x  = TRUE)
visits <- merge(visits,reshpg,by="id", all.x = TRUE)

visits[is.na(visits)] <- 0
visits$tot_visitors <- visits$air_visitors + visits$hpg_visitors
visits$tot_reserves <- visits$air_reserves + visits$hpg_reserves
visits$avg_anticipation <- (visits$air_anticipation + visits$hpg_anticipation) / 2
```


## Training and Testing model

Cargando librerías
```{r message==FALSE}
library(caret)
library(Metrics)
```

Obtención del train y del test

```{r}
# General data set
recruit_visits <- visits
factor_vars <- c('day_of_week','month_name','holiday_flg','golden_week',
                 'air_genre_name','city','ward','place','hpg_system')
recruit_visits[factor_vars] <- lapply(recruit_visits[factor_vars], function(x) as.factor(x))
tail(recruit_visits)
summary(recruit_visits)

# Split train and test data
until_train <- "2017-03-15"
train<-recruit_visits[as.Date(recruit_visits$visit_date) <= until_train,]
test<-recruit_visits[as.Date(recruit_visits$visit_date) > until_train,]
#nrow(train) + nrow(test)

rmColumns <- c("id","air_store_id","visit_date","air_reserves",
               "air_anticipation","hpg_reserves","hpg_anticipation",
               "tot_reserves","avg_anticipation","place","air_visitors")
train<-train[, !colnames(train) %in% rmColumns] 
test<-test[, !colnames(test) %in% rmColumns] 
colnames(train)

```

Modelado y cargado

```{r}
set.seed(123)
fitControl<- trainControl(
  method="none"
)
gridXGB  <- expand.grid(nrounds = c(19),
                        max_depth = c(18),
                        eta = c(0.4), 
                        gamma = c(1),
                        colsample_bytree = c(0.75),
                        min_child_weight = c(12),
                        subsample = c(0.65))

model <- train(visitors~., data=train,
               trControl=fitControl,
               tuneGrid=gridXGB,
               method="xgbTree")
```

Error RMSLE del modelo
```{r}
pred = predict(model,newdata=test[,!(names(test) %in% c("visitors"))])
errorPred <- rmsle(test$visitors, round(pred,0))
print(paste0("RMSLE:",errorPred))
```

Importancia de las variables
```{r pressure, echo=FALSE}
importancia<-varImp(model)
importancia$importance
```